---
title: "Tutorial reproducibility"
author: 
  - "Lars Vilhuber"
  - "Marie Connolly"
date: 3 January 2025
---

```{r config,include=FALSE}
library(readr)
library(here)
library(knitr)
library(dplyr)
library(ggplot2)
library(qualtRics)

# qualtRics secrets are read from the environment:
# - QUALTRICS_API_KEY
# - QUALTRICS_BASE_URL
# Let's check that they are there:

message(Sys.getenv("QUALTRICS_BASE_URL"))


# Qualtrics data for Day 1:
# you can find this with all_surveys() %>% arrange(creationDate) %>% head()

QUALTRICS_FULL_URL <- "https://cornell.yul1.qualtrics.com/jfe/form"
QUALTRICS_DAY1 <- "SV_bBqbJ9cSSJdOBw2"

# Time when this was posted (discard anything before that)

QUALTRICS_DAY1_STIME <- "2025-01-03 00:00:00"

# Public Qualtrics URL for day 2

QUALTRICS_DAY2 <- "SHORTLY"

if (!dir.exists(here::here("data"))) {
  dir.create(here::here("data"))
}
```

::: {.panel-tabset}

## Follow along

[lars.vilhuber.com/p/assa2025/](https://lars.vilhuber.com/p/assa2025/)

## Survey 1

Please fill out this survey on background and skills, to provide us with information on who you are. It will help us improve the presentation, and make it more relevant for you.

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_DAY1)`>

### Results

```{r downloaddata,include=FALSE}
# download data to local location

data.raw <- fetch_survey(surveyID = QUALTRICS_DAY1, verbose = TRUE) 
data <- data.raw |>
        filter(Status != "Survey Preview") |>
        filter(Consent == "I agree that my data will be used in the manner described.") |>
        filter(StartDate > QUALTRICS_DAY1_STIME) |>
  # renaming variables
  select(StartDate,EndDate,Status,Finished,RecordedDate,ResponseId,Consent,Degree,JEL_primary,
         starts_with("JEL_secondary"),starts_with("Desktop_"),starts_with("Advanced_usage_"),
         starts_with("Programming_"),starts_with("Versioning_"))


```

```{r create_table, results='asis', include=TRUE,echo=FALSE,message=FALSE}

if ( nrow(data) >0 ) {
data |>
  select(Degree) |>
  group_by(Degree) |>
  summarise(Frequency=n()) |>
  ungroup() |>
  mutate(Percent = round(Frequency/nrow(data)*100,2)) -> data.table

data.table |> kable()
} else {
  cat("No data yet. Check back later.")
}

```

## Day 1

One of the following (or a linear combination):

- [Setting yourself up for reproducibility](https://larsvilhuber.github.io/day1-tutorial/)
- [How to correctly document a replication package](https://larsvilhuber.github.io/readme-presentation/)

## Survey 2

To identify what we should be speaking about on Day 2, please fill out this other survey:

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_DAY2)`>


## Day 2

One of the following (or a linear combination):

- [Reproducibility when some data are confidential](https://labordynamicsinstitute.github.io/reproducibility-confidential/) 
- [Advanced self-checking of reproducibility](https://larsvilhuber.github.io/self-checking-reproducibility/presentation/)




```{r, child=c(here::here('99-links.md'))}
```

:::

